Simple Approximation Algorithms for Partitional and Hierarchical Clustering

### 2015-05-11 tex/project.tex
Updated project write-up

\begin{figure*}[h]
\label{fig:hier_results}
\small
\begin{tabular}{ | l | l | l | l | l | l | l | }
\hline
	   & Time & Time & Time & Time & Time & Time \\ \hline
	Dataset & Ave Linking & Ward Linking & K-med & K-med logn ran & k-med ran & PAM logn ran \\ \hline
	Soybean & 0.0002 & 0.0002 & 0.286 & 0 & 0.294 & 0.167 \\ 
	Iris & 0.002 & 0.003 & 3.161 & 0.226 & 3.794 & 5.122 \\ 
	Gauss\_5\_5\_5 & 0.038 & 0.060 & 106.619 & 2.735 &120.893 & 147.137 \\
	Gauss\_5\_10\_5 & 0.099 & 0.096 & 383.854 & 10.259 & 383.298 & 494.554 \\
	%Gauss\_5\_50\_5 &  & & & & & \\
	Gaussian Average & 0.0858 & 0.0853 & 354.459 & 7.492 & 369.967 & 423.293 \\ 
	pmed5 &  N/A & N/A & 1.184 & 0.102 & 1.288 & 1.673   \\ 
	pmed25 & N/A & N/A & 279.334 & 5.011 & 306.684 & 312.503   \\ 
	pmedian avg & N/A & N/A &  87.355 & 1.957 & 94.548 & 101.576   \\ \hline
\end{tabular}
\vspace{0.2 cm}

\begin{tabular}{ | l | l | l | l | l | l | l | }
\hline
	   & F-Score & F-Score & F-Score & F-Score & F-Score & F-Score \\ \hline
	Dataset & Ave Linking & Ward Linking & K-med & K-med logn rand & K-med rand & PAM logn rand \\ \hline
	Soybean & 0.615 & 0.510 & 0.772 & 0.643 & 0.742 & 0.633 \\ 
	Iris & 0.5 & 0.5 & 0.888 & 0.767 & 0.762 & 0.732 \\ 
	Gauss\_5\_5\_5 & 0.519 & 0.516 & 0.591 & 0.816 & 0.761 & 0.785 \\
	Gauss\_5\_10\_5 & 0.298 & 0.289 & 0.589 & 0.584 & 0.576 & 0.446 \\
	%Gauss\_5\_50\_5 &  & & & & & \\
	Gaussian Average & 0.393 & 0.375 & 0.649 & 0.616 & 0.624 & 0.624 \\ \hline
\end{tabular}
\vspace{0.2 cm}

@@

In general, the hierarchical framework performed significantly better than both methods of agglomerative clustering in terms of FScore measure, even for our logarithmic version. The FScore measures were very low for the agglomerative clustering methods, often around 0.25, but were much closer to the AMI measures we saw in flat clustering for our implemented algorithms.

@@

In the future, we hope to explore how linear programming based methods perform in both the flat and hierarchical context as well and to implement our own agglomerative clustering to test on the OR library instances and help make smarter local merges in the nesting framework.

>>>>

\begin{figure*}[h]
\label{fig:hier_results}
\small
\begin{tabular}{ | l | l | l | l | l | l | l | }
\hline
	   & Time & Time & Time & Time & Time & Time \\ \hline
	Dataset & Ave Linkage & Ward Linkage & K-med & K-med logn ran & k-med ran & PAM logn ran \\ \hline
	Soybean & 0.0004 & 0.0002 & 0.286 & 0 & 0.294 & 0.167 \\ 
	Iris & 0.0021 & 0.0011 & 3.161 & 0.226 & 3.794 & 5.122 \\ 
	Gauss\_5\_5\_5 & 0.0097 & 0.0109 & 106.619 & 2.735 &120.893 & 147.137 \\
	Gauss\_5\_10\_5 & 0.0237 & 0.0256 & 383.854 & 10.259 & 383.298 & 494.554 \\
	%Gauss\_5\_50\_5 &  & & & & & \\
	Gaussian Average & 0.0229 & 0.0239 & 354.459 & 7.492 & 369.967 & 423.293 \\ 
	pmed5 &  0.0004 & N/A & 1.184 & 0.102 & 1.288 & 1.673   \\ 
	pmed25 & 0.0174 & N/A & 279.334 & 5.011 & 306.684 & 312.503   \\ 
	pmedian avg & 0.0067 & N/A &  87.355 & 1.957 & 94.548 & 101.576   \\ \hline
\end{tabular}
\vspace{0.2 cm}

\begin{tabular}{ | l | l | l | l | l | l | l | }
\hline
	   & F-Score & F-Score & F-Score & F-Score & F-Score & F-Score \\ \hline
	Dataset & Ave Linkage & Ward Linkage & K-med & K-med logn rand & K-med rand & PAM logn rand \\ \hline
	Soybean & 0.615 & 0.554 & 0.772 & 0.643 & 0.742 & 0.633 \\ 
	Iris & 0.5 & 0.5 & 0.888 & 0.767 & 0.762 & 0.732 \\ 
	Gauss\_5\_5\_5 & 0.519 & 0.520 & 0.591 & 0.816 & 0.761 & 0.785 \\
	Gauss\_5\_10\_5 & 0.298 & 0.281 & 0.589 & 0.584 & 0.576 & 0.446 \\
	%Gauss\_5\_50\_5 &  & & & & & \\
	Gaussian Average & 0.393 & 0.378 & 0.649 & 0.616 & 0.624 & 0.624 \\ \hline
\end{tabular}
\vspace{0.2 cm}

@@

In general, the hierarchical framework performed significantly better than both methods of agglomerative clustering in terms of FScore measure, even for our logarithmic version. The FScore measures were very low for the agglomerative clustering methods, sometimes around 0.25, but were much closer to the AMI measures we saw in flat clustering for our implemented algorithms.

@@

In the future, we hope to explore how linear programming based methods perform in both the flat and hierarchical context as well and to implement our own agglomerative clustering to help make smarter local merges in the nesting framework.
